Handling String-Number Conversion in String Constraint Solving

### 2019-11-14 draft.tex
some fix 5.4 and add 5.5 to handle string length

\todo{Maybe talk about the heuristic that we merge the list elements into one}

@@

$$\begin{array}{rl}
\mathsf{epsilonAfter(k)}\defeq& (0\leq v_0,\ldots, v_k\leq 9) \wedge\\
&v_{k+1}=\ldots =v_m = -1\\
\mathsf{toNumber(k)}\defeq& (n = v_0\times 10^{k} + v_1\times 10^{k-1} + \ldots + v_{k})
\end{array}
$$

The function $\mathsf{epsilonAfter(k)}$ forces the first $k$ variables to be assigned some number and those after $k$ be assigned $\epsilon$. Recall that we use $-1$ to represent $\epsilon$. The function $\mathsf{toNumber(k)}$ converts the first $k$ variables to the corresponding number in $n$.
Then we can specify the relation between $n$ and the character variables as follows:
$$\Psi_n\defeq (n=-1 \vee \bigvee_{k\in [0,m]} (\mathsf{epsAfter(k)} \wedge \mathsf{toNumber(k)} ) )$$
It says either $x$ is not a number and so $n=-1$ or the first $k$ variables represent the value of $n$, for some $k\in [0,m]$. 
We add $\Psi_n$ to $\Phi_O$.

@@

\begin{lemma}\label{lemma:sticorrect_neg}
	$\semof {\Psi_n \wedge \parikhfof {A_x} \wedge (v_0 = 0)\wedge (n = -1) }_{V_x \cup \#V_x \cup \{n\}} = \{I_n\mid (I_n(n) = -1\} \times \semof {\parikhfof {A_x} \wedge (v_0 = 0) }_{V_x \cup \#V_x} $
\end{lemma}
In this case, $x$

>>>>

@@

$$\begin{array}{rl}
\mathsf{epsilonAfter(k)}\defeq& (0\leq v_1,\ldots, v_k\leq 9) \wedge\\
&v_{k+1}=\ldots =v_m = -1\\
\mathsf{toNumber(k)}\defeq& (n = v_1\times 10^{k-1} + v_2\times 10^{k-2} + \ldots + v_{k})
\end{array}
$$

The function $\mathsf{epsilonAfter(k)}$ forces the first $k$ variables to be assigned some number and those after $k$ be assigned $\epsilon$. Recall that we use $-1$ to represent $\epsilon$. The function $\mathsf{toNumber(k)}$ converts the first $k$ variables to the corresponding number in $n$. \yfc{say shifting $\epsilon$ to the right will not change the language}

The condition that when $x$ is ``not a number'' is specified by the following formula.

$$\Psi_{NaN} \defeq  \bigvee_{i\in [1,m]} v_i>9$$

Then we can specify the relation between $n$ and the character variables as follows:
$$\Psi_n\defeq  (n=-1 \wedge \Psi_{NaN})\vee \bigvee_{k\in [0,m]} (\mathsf{epsAfter(k)} \wedge \mathsf{toNumber(k)} )$$
It says either $x$ is not a number and so $n=-1$ or the first $k$ variables represent the value of $n$, for some $k\in [0,m]$. 
We add $\Psi_n$ to $\Phi_O$.

@@

\begin{lemma}\label{lemma:sticorrect_neg}
	$\semof {\Psi_n \wedge \parikhfof {A_x} \wedge (v_0 = 0)\wedge (n = -1) }_{V_x \cup \#V_x \cup \{n\}} = 
	\{(I\cup\pim \cup I_n) \mid  I_n(n)= -1 \wedge \decode {A_x}(I\cup\pim) \in [0,9]^+  \}$
\end{lemma}
In this case, $x$ does not encode a number. The lemma says  the models we add to $\Phi_O$ represents words in both $\semof{A_x}$ and $[0,9]^+$, which means not a number, and $n$ is $-1$.

\subsection{Handling the lengths of variables}
After the set $\Phi_I$ becomes empty, we start to add constraints to $\Phi_O$ to relate the lengths of string variables and their PFA. To do so, we first define $\Phi_{V_x}$ that describes the number of occurrences of each non-epsilon character variable in $x$.

$$\Phi_{V_x} \defeq \bigwedge_{v\in V_x} ( (s_v = 0 \wedge v = -1) \vee (s_v = \#v \wedge v \neq -1)) $$

More concretely, for each string variable $x$, we add linear formula $\Psi_{|x|}$ to $\Phi_O$.

$$\Phi_{|x|} \defeq \Phi_{V_x}  \wedge |x| =  \sum_{v\in V_x}  s_v $$
